\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-10 paper.qmd
Added references for Section 6

By visualizing the model of different layouts in $4\text{-}D$ reveal different characteristics of each NLDR method. When examining the model of a specific cluster, which appears more like a filled-out shape in tSNE, and UMAP, while the model has a pancake shape in PaCMAP. The reason to have filled-out shaped clusters in tSNE and UMAP is that the ability of capture the local structure. On the other hand, the reason for the pancake shape in PaCMAP is the fail to capture the local structure.

>>>>

By visualizing the model of different layouts in $4\text{-}D$ reveal different characteristics of each NLDR method. When examining the model of a specific cluster, which appears more like a filled-out shape in tSNE (@fig-five-gau-projs (a2, a3)), and UMAP (@fig-five-gau-projs (b2, b3)), while the model has a pancake shape in PaCMAP (@fig-five-gau-projs (c2, c3)). The reason to have filled-out shaped clusters in tSNE and UMAP is that the ability of capture the local structure. On the other hand, the reason for the pancake shape in PaCMAP is the fail to capture the local structure.

### 2024-09-10 paper.tex
Added references for Section 6

By visualizing the model of different layouts in \(4\text{-}D\) reveal
different characteristics of each NLDR method. When examining the model
of a specific cluster, which appears more like a filled-out shape in
tSNE, and UMAP, while the model has a pancake shape in PaCMAP. The
reason to have filled-out shaped clusters in tSNE and UMAP is that the
ability of capture the local structure. On the other hand, the reason
for the pancake shape in PaCMAP is the fail to capture the local
structure.

>>>>

By visualizing the model of different layouts in \(4\text{-}D\) reveal
different characteristics of each NLDR method. When examining the model
of a specific cluster, which appears more like a filled-out shape in
tSNE (Figure~\ref{fig-five-gau-projs} (a2, a3)), and UMAP
(Figure~\ref{fig-five-gau-projs} (b2, b3)), while the model has a
pancake shape in PaCMAP (Figure~\ref{fig-five-gau-projs} (c2, c3)). The
reason to have filled-out shaped clusters in tSNE and UMAP is that the
ability of capture the local structure. On the other hand, the reason
for the pancake shape in PaCMAP is the fail to capture the local
structure.
